Positional entropy in childes

### 2018-08-30 positional_entropy_childes.Rmd
CE and MI for non-English, plus English letter entropy (without graphs)

@@

ggplot(ce[[3]], aes(x = X, y = ce, color = as.factor(Y))) + 
  facet_wrap(~ length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Conditional entropy vs. conditioned random variable (utterances of length 5)")

>>>>

counts <- map(2:6, ~get_counts("not child", .x, brown_utterances))

@@

ggplot(ce, aes(x = X, y = ce, color = as.factor(Y))) + 
  facet_wrap(~ length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Conditional entropy vs. conditioned random variable (utterances of length 5)")
